More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-01-07 2016-Weak-FH-Bisim/WeakBisim.tex
lemma 5 tentative

\item similarly for tau transitions on states named $u$.

\item Similarly, for the open transition $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {\ostate{t} \OTarrow {\alpha} \ostate{t'}}$\\
If $Q$ moves then we  obtain by Lemma \ref{lem-decompose}:\\
$
		P\models{\openrule
			{
				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred}\,',  
				{\Post}\,'}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
	Q\models{\openrule
			{
				\beta_j^{j\in J\cap\Holes(Q)}, {\Pred}\,'',  
				{\Post}\,''}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$\\
such that  $\Pred^2 \iff {\Pred}\,'
		\land {\Pred}\,''\land \alpha'=\beta_{j_0}$, $\Post^2={\Post}\,'\uplus 
		{\Post}\,''$ where ${\Post}\,''$ is the restriction of $\Post^2$ over variables of $\Leaves(Q)$.

@@

\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from case 1 and 2 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}

\TODO{We will add side conditions ?? }\\
Concerning $Q$ if it moves, for each  $\symb{OT}_p$ of $Q$ such that $p \in S$ and $S \subseteq [0\ldots (m_1\!+\!m_2)\!+\!1]$ in the form:
\begin{mathpar}
Q\models{\openrule
			{
				(\beta_p)_j^{J_p}, {\Pred_p},  
				{\Post_p}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]

@@

\TODO{END???}

>>>>

\item Similarly for tau transitions on states named $u$.

\item And, for the open transition $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {\ostate{t} \OTarrow {\alpha} \ostate{t'}}$\\
If $Q$ moves then we  obtain by Lemma \ref{lem-decompose}:\\
$
		P\models{\openrule
			{
				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred}\,',  
				{\Post}\,'}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
	Q\models{\openrule
			{
				\beta_j^{j\in J\cap\Holes(Q)}, {\Pred}\,'',  
				{\Post}\,''}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$\\
such that  $\Pred^2 \iff {\Pred}\,'
		\land {\Pred}\,''\land \alpha'=\beta_{j_0}$, $\Post^2={\Post}\,'\uplus 
		{\Post}\,''$ where ${\Post}\,''$ is the restriction of $\Post^2$ over variables of $\Leaves(Q)$.

@@

\end{enumerate}

By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from case 1 and 2 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}

\TODO{We will add side conditions ?? }\\

Concerning $Q$, we consider only the paths for which it moves. So for each, state such that we have $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}}$, we skip the state $\ostate{({s}_{(p+1) l})^{l\in L_Q}}$ and  we rename all its following states  $\ostate{(s_{p})_l^{l\in L_Q}}$ by $\ostate{({s}_{(p-1) l})^{l\in L_Q}}$. We proceed in the same way as for states named $u$.

Therefore, we will obtain:

$\forall p \in [0\ldots n_1] Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
				{{\Post_p}\!\!''}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}%\]
$
and
$ Q\models{\openrule
			{
				\beta_j^{j\in J\cap\Holes(Q)}, {\Pred}\,'',  
				{\Post}\,''}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$
and
$\forall p \in [0\ldots n_2] Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
				{{\Post_p}\!\!''}}
				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha'_{p}}
				\ostate{u_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\
such that $n_1 \leq m_1$ and $n_2 \leq m_2$\\
\TODO{We will discuss}

For each  $\symb{OT}_p$ of $Q$ such that $p \in S$ and $S \subseteq [0\ldots (m_1\!+\!m_2)\!+\!1]$ in the form:
\begin{mathpar}
Q\models{\openrule
			{
				(\beta_p)_j^{J_p}, {\Pred_p},  
				{\Post_p}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]

@@
